Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-04-15 paper/main.tex
revise introduction

% Vorgabe < 110 chars incl. spaces
%  jetzt 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description}
% alt:BOLD responses of the Parahippocampal Place Area correlate with spatial cues in a movie and it's audio-only variant

@@

\begin{abstract}
% < 170 words
% new analysis of existing data
% of interest to a broad section of our audience
% highlighting innovative examples of data reuse
% may be used to present compelling new findings & conclusions derived from published data.
% submissions should exemplify reproducible research by clearly describing all steps in the analysis
% providing supporting source code, and explaining how and where others may access all data underlying the analysis.
Intro: PPA as classic example for an visual area
Methods: fMRI data, studyforrest data set, general linear model
Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
Conclusions: PPA nicht exclusively
\end{abstract}
% Intro + Discussion = main text ~ 3,000 words.
% include figure providing schematic overview of the study and assay(s) design
% -> ist overkill; Paradigma ist mit "Film ab" wenig kompliziert.
\section{Introduction}
% our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).

% yeah, whatever. Arbeite erstmal mit der references.bib
% und habe oben '\usepackage{natbib}' eingefügt
Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks. Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external \citep{westfall2016fixing} as well as ecological validity \citep{hasson2004intersubject}.
Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. \citep{dubois2016building})

% Retrosplenial-Cortex kommt in der jetzigen Einleitung nicht vor, jedoch in Ergebnissen von Movie & Audio-Description
% Muss spätestens in der Discussion diskutiert werden
% bin auch am überlegen, ob ich in den Ergebnissen zu den sagitallen slices durch die PPAs noch sagitale Slices durch die RSCs dazunehme??
A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream \citep{mishkin1982contribution, goodale1992separate}. Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
Results generalize at a group average level to a) mental imagination of landscapes \citep{ocraven2000mental} and b) haptic exploration of scenes \citep{wolbers2011modality}, \todo{this needs some more glue. the following is not just about spoken stimuli} whereas results of a study using spoken, place-related sentences were unclear \todo{should be more specific. unclear could mean 'not well described'} \citep{aziz2008modulation}:
a) In a study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures. The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.
% Wolbers im Folgenden macht noch ne Connectivitäts-Analyse mit dem Occipital-Cortex; da ist dann keine Connectivity im Vergleich zum visuellen Paradigma; deshalb kann das laut ihm kein mental image sein: "the scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
b) In a block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.
% Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
c) To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences. Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw''). Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact. Surprisingly, activation in the left, but not right, PPA was significantly reduced \todo{reduced relative to what condition?} when participants listened to place-related sentences. Moreover, this effect was only observed in sentences involving famous places.
% Frage: Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann in der Discussion diskutieren, was ggf. gar nicht nötwendig ist, weil's darum im Grunde nicht geht
In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information. This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general \citep{aminoff2006parahippocampal} for a review). Independent(ly) from competing theories (s. \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.

% coolness-faktor von natural stimuli ist in der Einleitung beinahe komplett raus
% data-driven analyses vs. theory-driven analyses ist komplett raus
% kann man in discussion bringen, muss man aber nicht ist ja dann offensichtlich
All studies reviewed above used a small set of carefully designed, simplified stimuli to strictly control experimental conditions. They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention. Thus, they cannot / could answer the question how the PPA might behave under life-like conditions. Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012notlost, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
% hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
In an early study \citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}. These time points correlated with increased hemodynamic activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
% hier wird ISC als solches nicht erwähnt
\citep{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}. fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames. Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
Both studies suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert]. Nevertheless, none of the reviewed study could investigate how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

% ich habe einiges deiner Kommentare versucht einzubauen
% wenn dir etwas nicht explizit genug ist, fühl dich, frei mir auf die Finger zu hauen oder es vorzugsweise bei wenig Aufwand direkt umzuformulieren;
% bzgl. open source habe ich nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen
% MIH:
% 1. is such stimulus (more) suitable for distinguishing this cognitive process from others?
% 2. given its suitability how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% 1) complex visual stimulation without a task, and
% 2) complex auditory stimulation without an explicit imagery task
% both aspects together can then be discussed in terms of the feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
In this study, we analyze data of three publicly available datasets from the same set of 15 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily investigate how the parrahippocampal gyrus responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and it's audio-description of same length \citep{hanke2014audiomovie}. Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}. Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task. We annotated events of the otherwise unknown temporal structure of both stimuli to be able to fit a theory-driven model. In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events. Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut. In/for the audio-description, we annotated clues about the missing visual content given by the narrator \citep{haeusler2020spechanno}. We correlated regressors drawn from the annotations in order to detect possible/possibly confounded regressors that might prevent functional isolation of the PPA. In conformity to the analyses performed in the studies reviewed above, we submitted our regressors to a standard multi-level, voxel-wise general linear model (GLM). For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a ``visual area'' in visually impaired persons.

\todo[inline]{the last paragraph contains a bunch of methods already. I would reduce this to talk about
the general approach: annotation of events, investigation of model quality, cross-analysis of datasets.
Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is a concrete realization of that
promise}

\section{Methods}
% Ich habe die zwei Methodenteile gemerged und vor allem gekürzt;
% Einige Stellen sind aber sicherlich noch zu lange; denn im Zweifel habe ich es stehen gelassen
% Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in \citep{hanke2014audiomovie} and \citep{hanke2016simultaneous, sengupta2016extension}

@@

% generate-masks.py; DO NOT TOUCH!
% FOR GROUP:
% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
% 1. these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
% 2. from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
% FOR SUBJECTS:
% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
% 3. merge probabilistic occipital & temporal mask in subject space
%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
% 4. created subject-specific FOV from 4d 7t audio drama time series
%	(./sub-??/masks/ao_fov_mask.nii.gz)
% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
\section{Results (audio)}
\begin{itemize}
\item vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
\item   https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot
\end{itemize}

\section{Results (movie)}
\begin{itemize}
\item lore ipsum
\end{itemize}

% MIH the discussion should primarily be anchored on the points the introduction concludes with. From my POV there is no need (and likely no space) to discuss results by stimulus type. Issue like different impact of attentional focus etc can be brought up in the joint paragraph that discussed how such a factor could have differentially impacted the results -- and if that would matter.
\section{Discussion (audio)}

\begin{itemize}
\item Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that leaves a much larger margin for inter-individual differences in imagining scenery, as well as actors' character and personality traits, while still preserving the time-locked presentation of information to a listener. At the same time, an auditory stimulus limits the effect of an attentional focus on the selection of a subset of simultaneously occurring auditory events, in contrast to the selection of different parts of the visual field.
\item mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
\item Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
\item setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
\item  Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
\item object und (room)geo ist vermischt
\item Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
\end{itemize}

@@

\section*{General Discussion}
\begin{itemize}
\item "Abfall" einer Film-Messung
\item Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
\item CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
\item was sind für Film und Audiobook die Confounds?
\item Occipital Place Area (Nakamura, 2000), RSC
\item Natural stimuli like movies [hasson2008neurocinematics; sonkusare2019naturalistic] or narratives [honey2012not-lost; lerner2011topographic; silbert2014coupled] offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs. Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated [haeusler2016annotation; labs2015portrayed].
\item Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions. This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
\item aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
\end{itemize}

>>>>

% Titel-Vorgabe < 110 chars incl. spaces
%  jetzt 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description}

@@

\begin{abstract}
% < 170 words
% new analysis of existing data
% of interest to a broad section of our audience
% highlighting innovative examples of data reuse
% may be used to present compelling new findings & conclusions derived from published data.
% submissions should exemplify reproducible research by clearly describing all steps in the analysis
% providing supporting source code, and explaining how and where others may access all data underlying the analysis.
Intro: PPA as classic example for an visual area
Methods: fMRI data, studyforrest data set, general linear model
Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
Conclusions: PPA nicht exclusively
\end{abstract}
% Vorgabe: Intro + Discussion = main text ~ 3,000 words.
% include figure providing schematic overview of the study and assay(s) design
% -> ist overkill; Paradigma ist mit "Film ab" wenig kompliziert.
\section{Introduction}
% our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
% yeah, whatever. Arbeite erstmal mit der references.bib
% und habe oben '\usepackage{natbib}' eingefügt
Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks. Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external \citep{westfall2016fixing} as well as ecological validity \citep{hasson2004intersubject}.
Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. \citep{dubois2016building})

% Retrosplenial Cortex kommt in Einleitung nicht vor
% wird aufgrund der Ergebnisse AV und AO in Discussion diskutiert werden
% -> in den geplanten Abbildungen / Slices aber nicht zu sehen
A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream \citep{mishkin1982contribution, goodale1992separate}.
Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
% Überblick
At a group avergae level, results generalize to mental imagination of landscapes \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO blocks \citep{wolbers2011modality}.
% Egal, was ich folgend in der Überblick & später im Detail bzgl. Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein.
% So wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA abgeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences
% Fig 3 dort; im Grunde kommt da aber überall nur uneinheitliche Grütze raus
One study that used spoken, place-related sentences showed significantly decreased activation in the left and no modulation in the right-hemispheric PPA \citep{aziz2008modulation}.

% Im Einzelnen
In the study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.

% Folgend: Wolbers. Er hat noch ne Connectivitäts-Analyse mit dem Occipital Cortex gemacht. Zum visuellen Paradigma ist da dann keine keine Connectivity im Vergleich zum visuellen Paradigma. Seine Interpretation: Es kann keine mental imagery sein:
% "The scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
In the block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from LEGO bricks compared to haptically explored abstract geometric objects.

% Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
% wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert. Sonst wird hier im Detail Mist erzählt
To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences. Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw''). Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact. Surprisingly, activation in the left, but not right, PPA was significantly reduced when participants listened to place-related sentences compared to listening to face-related sentences. Moreover, this effect was only observed in sentences involving famous places.

% Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"
% muss man dann natürlich in der Discussion diskutieren,
% was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht
In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information. This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general \citep{aminoff2006parahippocampal} for a review). Independent(ly) from competing theories (s. \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.

% Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus
% Data-driven vs. theory-driven analyses ist komplett raus
% ggf. erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.
% -> vgl. Speech-Anno-Paper; in Discussion bringen
All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions. They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention. Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
% hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}

% Bartels (2004) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively. Employing a reverse intersubject correlation, \citep{hasson2004intersubject} took used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames.
Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

% Bzgl. Open Source der der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen

% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
% N=14 is inner join of AV & AO
\todo[inline]{
    The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
    annotation of events,
    investigation of model quality,
    cross-analysis of datasets.
    Possibly cite https://psyarxiv.com/sdbqv/
    and declare that this study is a concrete realization of that promise
}
In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description of the same length \citep{hanke2014audiomovie}.
We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator [citep{haeusler2020speechanno}].
In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

\section{Methods}
% Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in \citep{hanke2014audiomovie} and \citep{hanke2016simultaneous, sengupta2016extension}

@@

% generate-masks.py; DO NOT TOUCH!
% FOR GROUP:
% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
% 1. these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
% 2. from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
% FOR SUBJECTS:
% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
% 3. merge probabilistic occipital & temporal mask in subject space
%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
% 4. created subject-specific FOV from 4d 7t audio drama time series
%	(./sub-??/masks/ao_fov_mask.nii.gz)
% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
\section{Results (audio)}
% vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
% https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot

\section{Results (movie)}
lore ipsum

% MIH the discussion should primarily be anchored on the points the introduction concludes with. From my POV there is no need (and likely no space) to discuss results by stimulus type. Issue like different impact of attentional focus etc can be brought up in the joint paragraph that discussed how such a factor could have differentially impacted the results -- and if that would matter.
\section{Discussion (audio)}
% Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that leaves a much larger margin for inter-individual differences in imagining scenery, as well as actors' character and personality traits, while still preserving the time-locked presentation of information to a listener. At the same time, an auditory stimulus limits the effect of an attentional focus on the selection of a subset of simultaneously occurring auditory events, in contrast to the selection of different parts of the visual field.
% mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
% Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
% setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
% Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
% object und (room)geo ist vermischt
% Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.

@@

\section*{General Discussion}
% Data-driven vs. Analysis-Driven
% "Abfall" einer Film-Messung
% how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
% feasibility of (multi-dimensional) localizer development with naturalistic stimuli
% Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
% CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
% was sind für Film und Audiobook die Confounds?
% Occipital Place Area (Nakamura, 2000), RSC
% Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs. Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
% Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions. This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
% aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
